Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2025-05-12 autovi_paper.qmd
Add fig caption for the lineup, make paper more compact

```{r message=TRUE}
if (!file.exists("cached_data/autovi_checker_demo_print.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  checker$check()
  saveRDS(checker$..str..(), "cached_data/autovi_checker_demo_print.rds")
} else {
  cli::cli_h3(readRDS("cached_data/autovi_checker_demo_print.rds"))
}
```

@@

```{r fig-plot-pair, echo = TRUE, fig.height=2, fig.width=3, out.width="60%", fig.cap="True plot alongside one null plot, for quick comparison."}
checker$plot_pair()
```

@@

The resulting checker class can be employed analogously to the linear model case described in @sec-autovi-usage. For illustration, we fit a Poisson model in which the quadratic term of the predictor $x$ is intentionally omitted. This misspecification manifests as a pronounced U-shaped pattern in the lineup display, which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.

@@

```{r}
pois_checker$plot_lineup()
```

@@

```{r message = TRUE}
if (!file.exists("cached_data/autovi_glm_checker_demo_print.rds")) {
  pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"),
                               keras_model = get_keras_model("vss_phn_32"))
  pois_checker$check()
  saveRDS(pois_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
} else {
  cli::cli_h3(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
}
```

>>>>

```{r message=TRUE}
if (!file.exists("cached_data/autovi_checker_demo_print.rds")) {
  checker$keras_model <- get_keras_model("vss_phn_32") 
  checker$check()
  saveRDS(checker$..str..(), "cached_data/autovi_checker_demo_print.rds")
} else {
  cat(readRDS("cached_data/autovi_checker_demo_print.rds"))
}
```

@@

```{r fig-plot-pair, echo = TRUE, fig.height=2, fig.width=3, out.width="45%", fig.cap="True plot alongside one null plot, for quick comparison."}
checker$plot_pair()
```

@@

The resulting checker class can be employed analogously to the linear model case described in @sec-autovi-usage. For illustration, we fit a Poisson model in which the quadratic term of the predictor $x$ is intentionally omitted. This misspecification manifests as a pronounced U-shaped pattern in the lineup display (see @fig-pois-lineup), which is also successfully identified by the computer vision model, yielding a p-value substantially below the conventional threshold of 0.05.

@@

```{r fig-pois-lineup, fig.cap="A lineup of residual plots from Poisson generalized linear models, with the true residual plot at position 4, which displays a distinct U-shaped pattern. In contrast, the null plots show characteristics broadly consistent with well-behaved residuals from linear regression models.", fig.pos="H", out.width="80%"}
pois_checker$plot_lineup()
```

@@

```{r message = TRUE}
if (!file.exists("cached_data/autovi_glm_checker_demo_print.rds")) {
  pois_checker <- auto_pois_vi(glm(y ~ x, family = "poisson"),
                               keras_model = get_keras_model("vss_phn_32"))
  pois_checker$check()
  saveRDS(pois_checker$..str..(), "cached_data/autovi_glm_checker_demo_print.rds")
} else {
  cat(readRDS("cached_data/autovi_glm_checker_demo_print.rds"))
}
```

### 2025-05-12 autovi_paper.tex
Add fig caption for the lineup, make paper more compact

\begin{verbatim}
\end{verbatim}

\begin{verbatim}
-- <AUTO_VI object>
Status:
 - Fitted model: lm
 - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
    - Output node index: 1
 - Result:
    - Observed visual signal strength: 3.16 (p-value = 0.0396)
    - Null visual signal strength: [100 draws]
       - Mean: 1.274
       - Quantiles: 
          ╔══════════════════════════════════════════╗
          ║  25%   50%   75%   80%   90%   95%   99% ║
          ║0.802 1.111 1.575 1.666 1.919 2.657 3.348 ║
          ╚══════════════════════════════════════════╝
    - Bootstrapped visual signal strength: [100 draws]
       - Mean: 2.795 (p-value = 0.05941)
       - Quantiles: 
          ╔══════════════════════════════════════════╗
          ║  25%   50%   75%   80%   90%   95%   99% ║
          ║2.455 2.941 3.177 3.300 3.474 3.537 3.668 ║
          ╚══════════════════════════════════════════╝
    - Likelihood ratio: 0.7333 (boot) / 0.06284 (null) = 11.67 
\end{verbatim}

@@

\includegraphics[width=0.6\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}

@@

The resulting checker class can be employed analogously to the linear
model case described in Section~\ref{sec-autovi-usage}. For
illustration, we fit a Poisson model in which the quadratic term of the
predictor \(x\) is intentionally omitted. This misspecification
manifests as a pronounced U-shaped pattern in the lineup display, which
is also successfully identified by the computer vision model, yielding a
p-value substantially below the conventional threshold of 0.05.

@@

\begin{center}
\includegraphics[width=1\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/unnamed-chunk-7-1.pdf}
\end{center}

\begin{verbatim}
\end{verbatim}

\begin{verbatim}
-- <AUTO_POIS_VI object>
Status:
 - Fitted model: glm, lm
 - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
    - Output node index: 1
 - Result:
    - Observed visual signal strength: 4.875 (p-value = 0.009901)
    - Null visual signal strength: [100 draws]
       - Mean: 1.331
       - Quantiles: 
          ╔══════════════════════════════════════════╗
          ║  25%   50%   75%   80%   90%   95%   99% ║
          ║1.035 1.233 1.488 1.644 1.941 2.276 2.639 ║
          ╚══════════════════════════════════════════╝
    - Bootstrapped visual signal strength: [100 draws]
       - Mean: 5.51 (p-value = 0.009901)
       - Quantiles: 
          ╔══════════════════════════════════════════╗
          ║  25%   50%   75%   80%   90%   95%   99% ║
          ║5.330 5.505 5.698 5.735 5.830 5.903 6.013 ║
          ╚══════════════════════════════════════════╝
    - Likelihood ratio: 0.05096 (boot) / 0 (null) = Extremely large 
\end{verbatim}

>>>>

\begin{verbatim}
<AUTO_VI object>
 Status:
  - Fitted model: lm
  - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
     - Output node index: 1
  - Result:
     - Observed visual signal strength: 3.16 (p-value = 0.0396)
     - Null visual signal strength: [100 draws]
        - Mean: 1.274
        - Quantiles: 
           ╔══════════════════════════════════════════╗
           ║  25%   50%   75%   80%   90%   95%   99% ║
           ║0.802 1.111 1.575 1.666 1.919 2.657 3.348 ║
           ╚══════════════════════════════════════════╝
     - Bootstrapped visual signal strength: [100 draws]
        - Mean: 2.795 (p-value = 0.05941)
        - Quantiles: 
           ╔══════════════════════════════════════════╗
           ║  25%   50%   75%   80%   90%   95%   99% ║
           ║2.455 2.941 3.177 3.300 3.474 3.537 3.668 ║
           ╚══════════════════════════════════════════╝
     - Likelihood ratio: 0.7333 (boot) / 0.06284 (null) = 11.67
\end{verbatim}

@@

\includegraphics[width=0.45\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-plot-pair-1.pdf}

@@

The resulting checker class can be employed analogously to the linear
model case described in Section~\ref{sec-autovi-usage}. For
illustration, we fit a Poisson model in which the quadratic term of the
predictor \(x\) is intentionally omitted. This misspecification
manifests as a pronounced U-shaped pattern in the lineup display (see
Figure~\ref{fig-pois-lineup}), which is also successfully identified by
the computer vision model, yielding a p-value substantially below the
conventional threshold of 0.05.

\includegraphics[width=0.8\textwidth,height=\textheight]{autovi_paper_files/figure-pdf/fig-pois-lineup-1.pdf}

\caption{\label{fig-pois-lineup}A lineup of residual plots from Poisson
generalized linear models, with the true residual plot at position 4,
which displays a distinct U-shaped pattern. In contrast, the null plots
show characteristics broadly consistent with well-behaved residuals from
linear regression models.}

\begin{verbatim}
<AUTO_POIS_VI object>
 Status:
  - Fitted model: glm, lm
  - Keras model: (None, 32, 32, 3) + (None, 5) -> (None, 1)
     - Output node index: 1
  - Result:
     - Observed visual signal strength: 4.875 (p-value = 0.009901)
     - Null visual signal strength: [100 draws]
        - Mean: 1.331
        - Quantiles: 
           ╔══════════════════════════════════════════╗
           ║  25%   50%   75%   80%   90%   95%   99% ║
           ║1.035 1.233 1.488 1.644 1.941 2.276 2.639 ║
           ╚══════════════════════════════════════════╝
     - Bootstrapped visual signal strength: [100 draws]
        - Mean: 5.51 (p-value = 0.009901)
        - Quantiles: 
           ╔══════════════════════════════════════════╗
           ║  25%   50%   75%   80%   90%   95%   99% ║
           ║5.330 5.505 5.698 5.735 5.830 5.903 6.013 ║
           ╚══════════════════════════════════════════╝
     - Likelihood ratio: 0.05096 (boot) / 0 (null) = Extremely large
\end{verbatim}

@@
